{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed Object Tracking

### 2017-11-28 wacv_for_review.tex

{\it YoungWoo : Particle filter smoothen the translations in between the
transitions. We want to reduce drifts from scale filter by having $R_{t}^{L}$, and
we want to reduce drifts from $R_{t}^{L}$ by having $R_{t}^{S}$. The particle filter
on the other hand aims at reducing the drifts and jumps further by bringing in the 
motion information.}
\end{comment}  
As explained earlier, the {\it E}nKCF updates a target's translation
at every other $k$ frames, particularly for estimating the target's
scale. Although the strategy of updating every other $k$th frames will
result in an optimal run-time performance, this may lead drifts at the
later frames. To prevent such potential drifts, we developed a Bayes
filter that incorporates a target's motion to smooth any intermediate
outputs from individual KCFs. In particular, we use a particle filter
to estimate the target's image coordinate based on the {\it E}nKCF's
outputs. The state in this paper, $\mathbf{X_t}$, represents the
target's pixel coordinates and its velocity, $\mathbf{X_t} = \lbrace
x, y, v_{x}, v_{y} \rbrace$, where $x$ and $y$ are the pixel
coordinates of the target's centroid, $v_x$ and $v_y$ are the velocity
estimated along the $x$-axis and $y$-axis. The particle filter
predicts, using a constant velocity motion model, a target's next
state by generating a predefined number of particles. Then it uses the
confidence maps of {\it E}nKCF as observation to update the state. The
weight of a particle is computed as, $w_{p_{t}}(x_{t},y_{t}) =
\sum_{i=1}^{N}\sum_{j=1}^{M} \mathbf{y_{R}}(x_{t}-i,y_{t}-j)$, where
$w_{p}$ denotes the weight of the particle $p$ at time $t$, and $N$
and $M$ denote the size of rows and columns of the confidence map.

\begin{comment}
We chooses some particles based on their importance to estimate the
target's next state, i.e., its pixel coordinates as $\hat{X}_{t} =
\sum_{p=1}^{P}w_{p_{t}} X_{t}.$ Note that, unlike a typical operation
of a particle filter, we skip the importance re-sampling step when the
scale filter, $R_{s}$, estimates the target's scale change. This is
because we observe the confidence map from the scale filter, $R_s$ is
sometime noisy. In addition, at every iteration, we check the variance
in the velocity components of the particles to re-assign velocities
from uniform initial distribution to keep variance high enough.
\end{comment}

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
We evaluate, using the object tracking benchmark datasets, the
performance of the proposed algorithm {\it E}nKCF and its variants.
Particularly, we choose two publicly, available datasets:
OTB100\footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and
UAV123\footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos about 100 objects
whereas UAV123 dataset contains aerial footages of 123 objects.  We
first evaluate the performance of {\it E}nKCF with two hand-crafted
features, fHoG and color-naming.  With this version, we would like to
have an object tracking algorithm that ``efficiently'' runs on an
embedded system, a drone, for example, in ``high speed,'' $\ge 30$
fps. Given this, we believe that the UAV123 dataset is a good fit in
evaluating the performance of the proposed algorithm. In addition, in
the UAV123 dataset, there are many challenging, realistic scenes,
e.g., abrupt scale/illumination changes. Although we are primarily
interested in developing an algorithm for mobile, embedded robotic
applications, it is also important to compare the performance of the
proposed algorithm with those of the state-of-the-art in a nominal
dataset. To this end, we chose the OTB100 dataset that contains the
videos recorded from smart phones and typical cameras in perspective
view. Also, we tested the proposed algorithm on a temporally
down-sampled version of the UAV123 dataset, called UAV123$\_$10fps
dataset. What we would like to evaluate using this modified dataset is
how robust the proposed algorithm is to the drastic motions of camera
and targets. Finally, we evaluate the Deep{\it E}nKCF, {\it E}nKCF
with deep features, on the UAV123 dataset to observe how much gain we
can achieve over hand-crafted features.

@@

%\textbf{Features Selections} We used different features for each of
%three KCFs as each of them has different goals to accomplish. In
%particular, the translation filter, $R_{t}^{L}$, uses both the fast
%Histograms of Oriented Gradients (fHoG) \cite{felzenszwalb2010object}
%and color-naming \cite{van2009learning} features to more effectively
%learn the background around the target as shown in Figure \ref{fig:Filters}. 
%Through experiments, we found that only fHoG didn't work well to cover a larger ROI; another
%translation filter, $R_{t}^{S}$, worked well when it used fHoG
%features only; the scale filter, $R_{s}$ did when it used both fHoG
%and color features.

\textbf{Performance on UAV123 Dataset} We used the precision and
success rate to compare the performance of the proposed algorithm with
those of the state-of-the-art, online algorithms for high speed
tracking. For the precision, we rank the trackers based on the
precision numbers at 20 pixels whereas in the success rate plots,
trackers are ranked based on area under curve (AUC) scores. The
tracking algorithms under the comparison include ones in high-speed
($\geq$300 fps): KCF \cite{henriques2015high}, CSK
\cite{henriques2012exploiting}, DCF \cite{henriques2015high}, MOSSE
\cite{bolme2010visual}, and STC \cite{zhang2014fast}
and ones in relatively lower-speed ($\geq$50): ECO \cite{DanelljanCVPR2017}, 
CCOT \cite{DanelljanECCV2016}, SCT \cite{Choi_2016_CVPR}, SAMF
\cite{li2014scale}, DSST \cite{danelljan2014accurate}, Struck
\cite{hare2012efficient}, MUSTER \cite{hong2015multi}, TLD
\cite{kalal2012tracking}, and OAB \cite{zhang2012robust}. The ECO and CCOT trackers
originally uses deep convolutional features. For the sake of fair comparison, we employ fHoG
and color-naming features similar to our study. Figure \ref{fig:UAV123_DATASET} shows 
the results on the UAV123 dataset. {\it  E}nKCF outperformed most of the high-speed tracking methods by
$3\%$-$15\%$ at 20 pixels precision. Three algorithms, SAMF, DSST, and
Struck did about $5\%$ better than ours in accuracy, but 10-20 times
slower. The more recent trackers, ECO and CCOT, on the other hand, outperforms
{\it  E}nKCF by $15\%$ while running at 10-15 times slower speed. 
For the scale adaptation, {\it E}nKCF did fourth best in terms
of AUC for the success rate plot. It outperformed other high-speed trackers
 by about $20\%$-$25\%$ in AUC. In addition, it performed even better than some of the lower-speed trackers. 
For example, for AUC, {\it E}nKCF outperformed Struck and DSST by $5\%$ and $10\%$ while running at more
than $10$ and $30$ times faster.

>>>>

{\it YoungWoo : Particle filter smoothen the translations in between the
transitions. We want to reduce drifts from scale filter by having $R_{t}^{L}$, and
we want to reduce drifts from $R_{t}^{L}$ by having $R_{t}^{S}$. The particle filter
on the other hand aims at reducing the drifts and jumps further by bringing in the 
motion information.}
\end{comment}  
As explained earlier, the {\it E}nKCF updates a target's translation
at every other $k$ frames, particularly for estimating the target's
scale. Although the strategy of updating every other $k$th frames will
result in an optimal run-time performance, this may lead drifts at the
later frames. To prevent such potential drifts, we developed a Bayes
filter that incorporates a target's motion to smooth any intermediate
outputs from individual KCFs. In particular, we use a particle filter
to estimate the target's image coordinate based on the {\it E}nKCF's
outputs. The state in this paper, $\mathbf{x_t}$, represents the
target's pixel coordinates and its velocity, $\mathbf{X_t} = \lbrace
x, y, v_{x}, v_{y} \rbrace$, where $x$ and $y$ are the pixel
coordinates of the target's centroid, $v_x$ and $v_y$ are the velocity
estimated along the $x$-axis and $y$-axis. The particle filter
predicts, using a constant velocity motion model, a target's next
state by generating a predefined number of particles. Then it uses the
confidence maps of {\it E}nKCF as observation to update the state. The
weight of a particle is computed as, $w_{p_{t}}(x_{t},y_{t}) =
\sum_{i=1}^{N}\sum_{j=1}^{M} \mathbf{y_{R}}(x_{t}-i,y_{t}-j)$, where
$w_{p}$ denotes the weight of the particle $p$ at time $t$, and $N$
and $M$ denote the size of rows and columns of the confidence map.

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
We evaluate the performance of the proposed algorithm {\it E}nKCF and
its variants using the object tracking benchmark
datasets. Particularly, we choose two publicly available datasets:
OTB100\footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and
UAV123\footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos of 100 objects whereas
UAV123 dataset contains aerial footages of 123 objects.  We first test
the {\it E}nKCF with two hand-crafted features, fHoG and color-naming.
With this version, our goal is to have an object tracking algorithm
that ``efficiently'' runs on an embedded system, a drone, in ``high
speed,'' $\ge 30$ fps. Given this goal, we believe that the UAV123
dataset is a good fit in evaluating the performance of the proposed
algorithm. In addition, in the UAV123 dataset, there are many
challenging, realistic scenes, e.g., abrupt scale/illumination
changes. Although we are primarily interested in developing an
algorithm for mobile, embedded robotic applications, it is also
important to compare the performance of the proposed algorithm with
those of the state-of-the-art in a nominal dataset. To this end, we
chose the OTB100 dataset that contains the videos recorded from smart
phones and typical cameras in perspective view. Also, we tested the
proposed algorithm on a temporally down-sampled version of the UAV123
dataset, called UAV123$\_$10fps dataset. What we would like to
evaluate using this modified dataset is how robust the proposed
algorithm is to the drastic motions of camera and targets. Finally, we
evaluate the Deep{\it E}nKCF, {\it E}nKCF with deep convolutional
features, on the UAV123 dataset to observe how much gain we can
achieve over the hand-crafted features.

@@

\textbf{Performance on UAV123 Dataset} We used the precision and
success rate to compare the performance of the proposed algorithm with
those of the state-of-the-art, online algorithms for high and low
speed tracking. For the precision, we rank the trackers based on the
precision numbers at 20 pixels whereas in the success rate plots,
trackers are ranked based on area under curve (AUC) scores. The
tracking algorithms under the comparison include ones in high-speed
($\geq$300 fps): KCF \cite{henriques2015high}, CSK
\cite{henriques2012exploiting}, DCF \cite{henriques2015high}, MOSSE
\cite{bolme2010visual}, and STC \cite{zhang2014fast} and ones in
relatively lower-speed ($\geq$50): ECO \cite{DanelljanCVPR2017}, CCOT
\cite{DanelljanECCV2016}, SCT \cite{Choi_2016_CVPR}, SAMF
\cite{li2014scale}, DSST \cite{danelljan2014accurate}, Struck
\cite{hare2012efficient}, MUSTER \cite{hong2015multi}, TLD
\cite{kalal2012tracking}, and OAB \cite{zhang2012robust}. The ECO and
CCOT trackers originally uses deep convolutional features, however,
for the sake of fair comparison, we employ fHoG and color-naming
features similar to our tracker. Figure \ref{fig:UAV123_DATASET} shows
the results on the UAV123 dataset. The {\it E}nKCF outperformed other
high-speed trackers by $3\%$-$15\%$ at 20 pixels precision. Three
algorithms, SAMF, DSST, and Struck did about $5\%$ better than ours in
accuracy, but 10-20 times slower. The more recent trackers, ECO and
CCOT, on the other hand, outperforms {\it E}nKCF by $15\%$ while
running at 10-15 times slower speed.  For the scale adaptation, {\it
  E}nKCF did fourth best in terms of AUC for the success rate plot. It
outperformed other high-speed trackers by about $20\%$-$25\%$ in
AUC. In addition, it performed even better than some of the
lower-speed trackers.  For example, for AUC, {\it E}nKCF outperformed
Struck and DSST by $5\%$ and $10\%$ while running at more than $10$
and $30$ times faster.
